---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(ggplot2)
library(plotly)
library(leaflet)
library(stringr)
library(glue)
library(magick)
.root <- rprojroot::is_rstudio_project$make_fix_file()
xfun::download_file("https://www.dropbox.com/s/2rryka3cprtgfok/heritageDataRevised.Rdata?dl=1", mode="wb")
load("heritageDataRevised.Rdata")
```

# define user, heritage structure
```{r}
# user structure
user <- 
  list(
    sessionData = 
      list(
        county_chosen = character(0),
        filtered_data = vector("list",0),
        game = 
          list(
            puzzle_guess = vector("list",0)
          )
      ),
    checkIns = vector("list",0),
    visits = vector("list",0)
  )
# heritage structure
heritage <-
  list(
    data = heritageData,
    show_county = function(){},
    filter = list(
      countyChosen = function(county){}
    ),
    game = list(
      puzzle_guess = function(){}
    ),
    validate_checkIn = function(returnedGPS){},
    track = function(list_tracks){}
  )
```
  
# show by county --------------------------------------------
# App function: user wants to zoom into map that shows only the point of interests belong to certain county
# when select choose by county on APP, it calls
heritage$show_county <- 
heritage$show_county() -> user$sessionData$county_chosen
# which returns a character vector of counties on screen
#  1. prompt names of counties that he can choose on screen
#  2. once chosen, return user's choice and save in the according object element

# Then program continues
heritage$filter$countyChosen <- 
heritage$filter$countyChosen(user$sessionData$county_chosen) -> 
  user$sessionData$filtered_data

# countyChosen returns caseIds that fit the chosen criterion.
# The backend return user$sessionData$filtered_data to the frontend which will redraw the map

# play puzzle -------------------------------------------------------------
# when user selects play puzzle guess, it calls
```{r}
heritage$game$puzzle_guess <- 
heritage$game$puzzle_guess() -> game_result
```

```{r}

test<-heritageData$belongCity[30]

puzzle_guess <-function(){
  
  message(paste0('1.easy','2.medium','3.hard'))
  level <- readline("choose level: ")
  original_pic<-get_original_pic(test)
  difficult <- c(3,5,9)
  lv<-difficult[as.numeric(level)]
  puzzle<-get_puzzle(lv,original_pic)
  time<- format_ISO8601(now(),usetz = T)
  answer<-photo
  
  return(timestamp(as.character(time)),
         answer(answer),
         opition(original_pic))
  
  
    
}


get_original_pic <-function(test){

  maybe_image<-list()
  city<-grepl(test,heritageData$belongCity)
  for (x in seq_along(heritageData$belongCity)){
    if(city[x]==TRUE){
      maybe_image[[length(maybe_image)+1]]<-heritageData$representImage[x]
      }}
    original_pic <- sample(maybe_image,1,replace = F)
    
    return(original_pic)
    }


get_photo<-function(original_pic){
  photo_URL<-as.character(original_pic)
  photo_URLencode<-URLencode(photo_URL)
  download.file(photo_URLencode,paste0('photo','.jpg'))
  photo<-image_read(photo_URLencode)
  return(photo)
 }
  
 
get_puzzle <- function(lv,original_pic){
  photo<-get_photo(original_pic)
  
  big<-image_info(photo)
  width <- big$width
  height <- big$height
  row_width<-width/lv
  col_height<-height/lv
  puzzle_store<-c()
  cut_row<-list()
  cut_col<-list()
    for (i in 0:(lv-1)){
      for (j in 0:(lv-1)) {
        cut_row[length(cut_row)+1]<-row_width*i
        cut_col[length(cut_col)+1]<-col_height*j
      }
    }
    for ( k in 1:length(cut_row)){
      puzzle_store[length(puzzle_store)+1]<-(image_crop(photo,glue("{row_width}","X","{col_height}","+","{cut_row[k]}","+","{cut_col[k]}")                                        ))}
  stack<-list()
  new_pic<-as.vector(puzzle_store)
  order<-sample(new_pic,(lv^2),F)
 for (g in 0:(lv-1)){
   p=order[(1+(lv*g)):(lv*(g+1))]
  stack[length(stack)+1]<-image_append(unlist(p),stack = F)
 }
  play_pic<-image_append(stack[1:length(stack)],attack=T)
  
  
  return(puzzle)}


  
    

  


```



#  the return is a list of elements: 
#  timestamp=a character of ISO8601 time when the user starts to play
#  answer=a caseId of correct answer
#  options=a character vector of caseIds of heritage options
#  and user_choice=a caseId of user's choice among options
# game_result$timestamp
# game_result$answer
# game_result$options
# game_result$user_choice
```{r}
# record result
user$sessionData$game$puzzle_guess <- 
  append(
    user$session$game$puzzle_guess,
    list(game_result)
  )
```




# check in ----------------------------------------------------------------
# user check in in the webapp UI, 
#browseURL("https://tpemartin.github.io/109-2-app101/checkin") 
# the frontend returns a numeric vector of GPS
# c(latitude=..., longitude=...)
returnedGPS = c(lon=24.94, lat=121.37)
heritage$validate_checkIn <- 
heritage$validate_checkIn(returnedGPS) -> checkInResult
# which check if the returnGPS is within 100 meters of any heritage site, 
# If not, checkInResult = NULL;
# If yes, 
# checkInResult = list(
#   timestamp= a string of ISO8601 time when the user checks in,
#   caseId= the closest site's caseId
# )
# sp::spDistsN1 can calculate km distance for you

if(!is.null(checkInResult)){
    user$checkIns <- append(
        user$checkIns, list(checkInResult)
    )
}


# track -------------------------------------------------------------------
# when user turn on tracking in the frontend, user's phone will track his GPX 
source(
  file.path(.root(),"R/field_trips_all.R")
)
# return user's list_tracks

heritage$track <-
heritage$track(list_tracks) -> 
  newTraces
# where newTraces is a list of length(list_tracks) for element 1, it transform list_trackes[[1]]
#list_tracks[[1]][c("lon","lat")] -> trace1
#newTraces <- list()
# newTraces[[1]] <- 
#   list(
#     timestamp=date of visit
#     trace=trace1,
#     caseId=
#   )

user$visits <- append(
  user$visits, newTraces
)